Optimization Methods for Parameter Identification \\ in Settings with Only Partial Knowledge

### 2023-06-08 presentation/iccopt22.tex
[FINAL SUBMITTED] The very final version of my thesis. Compiles clean.

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
\title{A Relaxation Approach to Feature Selection \newline for Linear Mixed-Effects Models}
\date{\today}
\author{Aleksei Sholokhov, James V. Burke, Peng Zheng, Damian Santomauro, and Aleksandr Aravkin}
\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

@@

Sparse Relaxed Regularized Regression ($\mathcal{SR}3$) \cite{Zheng2018RelaxAndSplit} showed great results for t linear models:

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \cite{Bondell2010,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \cite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\cite{Fan2001,Fan2012})
\end{itemize}

@@

%\begin{frame}{Value Function Reformulation}
%\begin{figure}
%	\includegraphics[width=\textwidth]{Figures/intuition_prev_paper}
%	\caption{\label{fig:intuition_prev} Picture from \cite{Zheng2018RelaxAndSplit}: for a linear problem, value function relaxation ``squashes'' level-sets simplifying the optimization landscape.}
%\end{figure}
%\end{frame}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset from~\cite{GBD}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

\begin{frame}{References}
	\textbf{References}: 
	\bibliographystyle{plain}
	\bibliography{bibliography.bib}
\end{frame}

>>>>

\usepackage{xspace}
\usepackage{caption}

\usepackage{subcaption}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
\title{A Relaxation Approach to Feature Selection \newline for Linear Mixed-Effects Models}
\date{\today}
\author{Aleksei Sholokhov, James V. Burke, Peng Zheng, Damian Santomauro, and Aleksandr Aravkin}
\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

@@

Sparse Relaxed Regularized Regression ($\mathcal{SR}3$) \footcite{Zheng2018RelaxAndSplit} showed great results for t linear models:

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \footcite{Krishna2008,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \footcite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\footcite{Fan2001,Fan2012})
\end{itemize}

@@

%\begin{frame}{Value Function Reformulation}
%\begin{figure}
%	\includegraphics[width=\textwidth]{Figures/intuition_prev_paper}
%	\caption{\label{fig:intuition_prev} Picture from \footcite{Zheng2018RelaxAndSplit}: for a linear problem, value function relaxation ``squashes'' level-sets simplifying the optimization landscape.}
%\end{figure}
%\end{frame}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset from~\footnote{Institute for Health Metrics and Evaluation (IHME). Bullying Victimization Relative Risk Bundle GBD 2020. Seattle, United States of America (USA), 2021.}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

\begin{frame}[noframenumbering,plain,allowframebreaks]{References}
    \printbibliography[heading=none]
\end{frame}

### 2023-06-08 presentation/phd_defense_pres.tex
[FINAL SUBMITTED] The very final version of my thesis. Compiles clean.

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lmodern}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
%\title{PhD Defense}
%\date{\today}
%\author{Aleksei Sholokhov}
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}
\title{Optimization Methods for Parameter Identification \\ in Settings with Only Partial Knowledge}
\subtitle{Ph.D. Defense}
\date{\today}
\author{Aleksei Sholokhov}
\titlegraphic{\vspace{3em}\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}}

@@

\section{$\mathcal{MSR}3$ -- Sparse Relaxed Regularized Regression for Linear Mixed-Effect Models}

@@

\begin{frame}[label=again]{Results: Kolmogorov Flow}
	A 2D velocity field $\bd{u}(x, y, t)$:

	\begin{align}
	\label{eq:kolmogorov_flow_definition}
	& \partial_t \bd{u} + \bd{u} \cdot \nabla \bd{u} = -\nabla p + \nu\nabla^2\bd{u} + f \\
	& \nabla \cdot \bd{u} = 0
	\end{align}
	where 
	\begin{itemize}
		\item $p$ is a 2D pressure field
		\item $f = \alpha\sin(ky)x$ - driving force with amplitude $A$ and wavenumber $k$ ($k=4$)
		\item $\nu = 1/\text{Re}$ is the non-dimensional viscosity. Re=40
	\end{itemize}
	\vspace{1em}
	Reconstruction with SPF rate = $0.18$\% (8 SPI samples per a frame of $66\times 66$ pixels):  
	\animategraphics[loop,width=\textwidth]{5}{Figures/kolm_example_anim_}{0}{19}
\end{frame}

@@

\againframe{again}

@@

\appendix
\section{Appendix: $\mathcal{MSR}3$}

>>>>

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}

\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
%\title{PhD Defense}
%\date{\today}
%\author{Aleksei Sholokhov}
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}
\title{Optimization Methods for Parameter Identification \\ in Settings with Only Partial Knowledge}
\subtitle{Ph.D. Defense}
\date{\today}
\author{Aleksei Sholokhov}
\titlegraphic{\vspace{3em}\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}}

@@

\section{\texorpdfstring{$\mathcal{MSR}3$}{MSR3} -- Sparse Relaxed Regularized Regression for Linear Mixed-Effect Models}

@@

\begin{frame}{Results: Kolmogorov Flow}
	A 2D velocity field $\bd{u}(x, y, t)$:

	\begin{align}
	& \partial_t \bd{u} + \bd{u} \cdot \nabla \bd{u} = -\nabla p + \nu\nabla^2\bd{u} + f \\
	& \nabla \cdot \bd{u} = 0
	\end{align}
	where 
	\begin{itemize}
		\item $p$ is a 2D pressure field
		\item $f = \alpha\sin(ky)x$ - driving force with amplitude $A$ and wavenumber $k$ ($k=4$)
		\item $\nu = 1/\text{Re}$ is the non-dimensional viscosity. Re=40
	\end{itemize}
	\vspace{1em}
	Reconstruction with SPF rate = $0.18$\% (8 SPI samples per a frame of $66\times 66$ pixels):  
	\animategraphics[loop,width=\textwidth]{5}{Figures/kolm_example_anim_}{0}{19}
\end{frame}

@@

%\againframe{again}

@@

\appendix
\section{Appendix: \texorpdfstring{$\mathcal{MSR}3$}{MSR3}}
